---
title: "getEquityLine() function"
author: "Paweł Sakowski"
date: "`r Sys.time()`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
      smooth_scrool: true
    number_sections: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, fig.width = 9)
```

# Loading packages and functions
```{r}
library(tidyverse)
library(xts)
library(dygraphs)
library(quantmod)
source("funs/getEquityLine.R")
source("funs/getPerformanceStats.R")
```

# Example1

## Data

```{r}
nObs <- 365
set.seed(1234)
quotes <-
  tibble(
    Date = seq(from = Sys.Date() - nObs + 1, to = Sys.Date(), by = 1) %>% as.Date()
  ) %>%
  mutate(
    eq1 = rnorm(nObs, 0, 0.01) %>% cumsum() %>% exp(),
    eq2 = rnorm(nObs, 0, 0.01) %>% cumsum() %>% exp(),
    eq3 = rnorm(nObs, 0, 0.01) %>% cumsum() %>% exp(),
    eq4 = rnorm(nObs, 0, 0.01) %>% cumsum() %>% exp()
  ) %>%
  mutate(eq1 = eq1/first(eq1)) %>%
  mutate(eq2 = eq2/first(eq2)) %>%
  mutate(eq3 = eq3/first(eq3)) %>%
  mutate(eq4 = eq4/first(eq4)) %>%
  pivot_longer(!Date) %>%
  rename(Price = value)
```

## Initial weights
```{r}
weightsList <- list()
weightsList[[1]] <- c(0.25, 0.25, 0.25, 0.25)
names(weightsList[[1]]) <- c("eq1", "eq2", "eq3", "eq4")
names(weightsList)[1] <- quotes %>% 
  head(1) %>% select(Date) %>% pull() %>% as.character()
weightsList
```

## Equity line
```{r}
quotes <- 
  quotes %>%
  bind_rows(
    getEquityLine(quotes, weightsList, 0, 1, 1) %>% 
      rename(Price = eqL) %>% 
      mutate(name = "eqL")
  )
```

## Visualisation

```{r eval = F}
quotes %>%
  ggplot(aes(Date, Price, col = name)) +
  geom_line()
```

```{r}
quotes.xts <- 
  quotes %>% 
  pivot_wider(names_from = name, values_from = Price) %>%
  select(-Date) %>%
  xts(order.by = quotes$Date %>% unique() %>% sort())

quotes.xts %>% 
  dygraph() %>%
  dyRangeSelector(height = 40)
```

## Performance stats
```{r}
quotes %>%
  pivot_wider(names_from = name, values_from = Price) %>%
  select_at(vars(starts_with("eq"))) %>%
  map_df(~ getPerformanceStats(., scale = 365), 
        .id = "eqline") %>%
  kableExtra::kable(
    caption = "Performance stats based on daily intervals",
    row.names = T, digits = 2, escape = F
  ) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive" ),
    full_width = T, font_size = 14
  )
```

where:

* aRC - Annualized Rate of Return (%), compounded daily
* aSD - Annualized Standard Deviation of daily returns (%),
* MD  - Maximum Drawdown (%),
* MLD - Maximum Loss Duration (in years),
* IR1 - Information Ratio, aRC/aSD,
* IR2 - IR1 * aRC * sign(aRC)/MD
* IR3 - aRC ^ 3 / (aSD * MD * MLD)
* nObs    - number of observations

# Example 2

## Data

```{r}
nObs <- 365
set.seed(1234)
quotes <-
  tibble(
    Date = seq(from = Sys.Date() - nObs + 1, to = Sys.Date(), by = 1) %>% as.Date()
  ) %>%
  mutate(
    eq1 = rnorm(nObs, 0.0005, 0.002) %>% cumsum() %>% exp(),
    eq2 = rnorm(nObs, 0.0004, 0.002) %>% cumsum() %>% exp(),
    eq3 = -rnorm(nObs, 0.0003, 0.002) %>% cumsum() %>% exp(),
    eq4 = -rnorm(nObs, 0.0002, 0.002) %>% cumsum() %>% exp(),
  ) %>%
  mutate(eq1 = eq1/first(eq1)) %>%
  mutate(eq2 = eq2/first(eq2)) %>%
  mutate(eq3 = eq3/first(eq3)) %>%
  mutate(eq4 = eq4/first(eq4)) %>%
  pivot_longer(!Date) %>%
  rename(Price = value)
```

## Initial weights
```{r}
weightsList <- list()
weightsList[[1]] <- c(0.25, 0.25, 0.25, 0.25)
names(weightsList[[1]]) <- c("eq1", "eq2", "eq3", "eq4")
names(weightsList)[1] <- quotes %>% 
  head(1) %>% select(Date) %>% pull() %>% as.character()
weightsList
```

## Equity line
```{r}
quotes <- 
  quotes %>%
  bind_rows(
    getEquityLine(quotes, weightsList, 0, 1, 1) %>% 
      rename(Price = eqL) %>% 
      mutate(name = "eqL")
  )
```

## Visualisation

```{r eval = F}
quotes %>%
  ggplot(aes(Date, Price, col = name)) +
  geom_line()
```

```{r}
quotes.xts <- 
  quotes %>% 
  pivot_wider(names_from = name, values_from = Price) %>%
  select(-Date) %>%
  xts(order.by = quotes$Date %>% unique() %>% sort())

quotes.xts %>% 
  dygraph() %>%
  dyRangeSelector(height = 40)
```

## Performance stats
```{r}
quotes %>%
  pivot_wider(names_from = name, values_from = Price) %>%
  select_at(vars(starts_with("eq"))) %>%
  map_df(~ getPerformanceStats(., scale = 365), 
        .id = "eqline") %>%
  kableExtra::kable(
    caption = "Performance stats based on daily intervals",
    row.names = T, digits = 2, escape = F
  ) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive" ),
    full_width = T, font_size = 14
  )
```

where:

* aRC - Annualized Rate of Return (%), compounded daily
* aSD - Annualized Standard Deviation of daily returns (%),
* MD  - Maximum Drawdown (%),
* MLD - Maximum Loss Duration (in years),
* IR1 - Information Ratio, aRC/aSD,
* IR2 - IR1 * aRC * sign(aRC)/MD
* IR3 - aRC ^ 3 / (aSD * MD * MLD)
* nObs    - number of observations


# Example 3

## Data

```{r}
nObs <- 365
set.seed(1234)
quotes <-
  tibble(
    Date = seq(from = Sys.Date() - nObs + 1, to = Sys.Date(), by = 1) %>% as.Date()
  ) %>%
  mutate(
    eq1 = seq(from = 1, to = 3, length.out = nObs),
    eq2 = seq(from = 1, to = 2, length.out = nObs),
    eq3 = seq(from = 1, to = 0, length.out = nObs),
    eq4 = seq(from = 1, to = 0, length.out = nObs)
  ) %>%
  mutate(eq1 = eq1/first(eq1)) %>%
  mutate(eq2 = eq2/first(eq2)) %>%
  mutate(eq3 = eq3/first(eq3)) %>%
  mutate(eq4 = eq4/first(eq4)) %>%
  pivot_longer(!Date) %>%
  rename(Price = value)
```

## Initial weights
```{r}
weightsList <- list()
weightsList[[1]] <- c(0.25, 0.25, 0.25, 0.25)
names(weightsList[[1]]) <- c("eq1", "eq2", "eq3", "eq4")
names(weightsList)[1] <- quotes %>% 
  head(1) %>% select(Date) %>% pull() %>% as.character()
weightsList
```

## Equity line
```{r}
quotes <- 
  quotes %>%
  bind_rows(
    getEquityLine(quotes, weightsList, 0, 1, 1) %>% 
      rename(Price = eqL) %>% 
      mutate(name = "eqL")
  )
```

## Visualisation

```{r eval = F}
quotes %>%
  ggplot(aes(Date, Price, col = name)) +
  geom_line()
```

```{r}
quotes.xts <- 
  quotes %>% 
  pivot_wider(names_from = name, values_from = Price) %>%
  select(-Date) %>%
  xts(order.by = quotes$Date %>% unique() %>% sort())

quotes.xts %>% 
  dygraph() %>%
  dyRangeSelector(height = 40)
```

## Performance stats
```{r}
quotes %>%
  pivot_wider(names_from = name, values_from = Price) %>%
  select_at(vars(starts_with("eq"))) %>%
  map_df(~ getPerformanceStats(., scale = 365), 
        .id = "eqline") %>%
  kableExtra::kable(
    caption = "Performance stats based on daily intervals",
    row.names = T, digits = 2, escape = F
  ) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive" ),
    full_width = T, font_size = 14
  )
```

where:

* aRC - Annualized Rate of Return (%), compounded daily
* aSD - Annualized Standard Deviation of daily returns (%),
* MD  - Maximum Drawdown (%),
* MLD - Maximum Loss Duration (in years),
* IR1 - Information Ratio, aRC/aSD,
* IR2 - IR1 * aRC * sign(aRC)/MD
* IR3 - aRC ^ 3 / (aSD * MD * MLD)
* nObs    - number of observations

